Preferences interact: what consequences for a Schelling scenario?

### 2019-11-07 ethnic_value_rum.Rmd
Add files via upload
added data, simplified check

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(plyr)
library(foreach)
library(dplyr)

@@

test <- read.csv("cond1.csv",sep = ",", skip = 6)
names(test) <- pull(read_csv("code_names.csv"))

@@

```{r  heatmap, include = FALSE, echo = FALSE}

dataset %>% filter(e_sqr == 30, v_crl == 30)

>>>>

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(plyr)
library(dplyr)

@@

mj_30_10 <- read.csv("80_g_30_10.csv",sep = ",", skip = 6)
names(mj_30_10) <- pull(read_csv("code_names.csv"))

eq_30_10 <- read.csv("50_g_30_10.csv",sep = ",", skip = 6)
names(eq_30_10) <- pull(read_csv("code_names.csv"))

@@

```{r gg }

eq_30_10 %>% filter(e_sqr == 30, v_crl == 10)
mj_30_10 %>% filter(e_sqr == 30, v_crl == 10)
